Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-07-27 ms.tex
plot the reference pixels during the 1.5 mA repeat 2
filled in LW LED info

\clearpage
\subsection{Asic Dewar Tests}
We performed a variety of stability tests using a dewar with the same type of detectors, readout electronics and temperature control as the in-flight parts.
The detectors and asic controllers are devices that did not fully meet the flight requirements for NIRCam, but in many cases are close or above requirements.
The detectors are illuminated by short wavelength LEDs (1.6 to 1.8~$\mu$m) or long wavelength (\textbf{Which type and wavelength?}) LEDs.
The LEDS are type Lms17 and ???? from Electro Optical Components, Inc.

The dewar has limited space for optical illumination so the LEDS light is bounced off a convex mirror and painted aluminum surface before reaching the detectors.
The convex mirror, its support structure and a black mask at the edges of the detectors all produce a shadows on some pixels of the detector.
The illuminated portions of the detector are used for aperture extractions while the shadows are used for background subtraction apertures.

@@

@@

\section{Expected In-Flight Performance with JWST}

>>>>

\clearpage
\subsection{Asic Dewar Tests}
We performed a variety of stability tests using a dewar with the same type of detectors, readout electronics and temperature control as the in-flight parts.
The detectors and asic controllers are devices that did not fully meet the flight requirements for NIRCam, but in many cases are close or above requirements.
The detectors are illuminated by short wavelength LEDs (1.6 to 1.8~$\mu$m) or long wavelength (3.0 to 3.6~$\mu$m) LEDs.
The LEDS are type LMS17LED-R and LMS34LED-R from Electro Optical Components, Inc.

The dewar has limited space for optical illumination so the LEDs' light is bounced off a convex mirror and painted aluminum surface before reaching the detectors.
The convex mirror, its support structure and a black mask at the edges of the detectors all produce a shadows on some pixels of the detector.
The illuminated portions of the detector are used for aperture extractions while the shadows are used for background subtraction apertures.

@@

\begin{figure*}
{\gridline{\fig{azstab_1p5mA_repeat_2_refpix}{0.99\textwidth}{}}}
\caption{Reference pixels cannot easily explain the trends between detectors.}\label{fig:refpixTSeries}
\end{figure*}

@@

\clearpage
\section{Expected In-Flight Performance with JWST}
